%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 9pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage[T1]{fontenc}
\usepackage[sc]{mathpazo} % Use the great palatino font provided by the mathpazo package. Add osf for old style figures
\usepackage{multicol}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\usepackage{color}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage[T1]{fontenc}

\setlength{\textwidth}{5.2in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------
\vspace{-10pt}
\moveleft.5\hoffset\centerline{\huge\bf Zheren Ma} % Your name at the top
\moveleft.5\hoffset\centerline{zhrm@utexas.edu, 512-8658134}
\moveleft.5\hoffset\centerline{Ph.D. Candidate in Mechanical Engineering with expertise in advanced control, scientific programming and data analytics}

\vspace{-5pt}

\moveleft\hoffset\vbox{\hrule width\resumewidth height .5pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
\vspace{-10pt}
%\moveleft.5\hoffset\centerline{\color{blue}{\url{http://yuhaozhu.com/}}}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	RESEARCH INTERESTS SECTION
%----------------------------------------------------------------------------------------

\vspace*{-5pt}
%\section{RESEARCH\\ INTERESTS}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\vspace*{-10pt}
\section{EDUCATION}

\textbf{Mechanical Engineering, The University of Texas at Austin} \hfill\textit{2013-present} \\
Ph.D. Candidate majoring in Dynamic Systems and Control,  GPA: 4.0/4.0 \\
\href{https://scholar.google.com/citations?user=EJJUXmMAAAAJ&hl=en}{Publications}: 3 IEEE/ASME journal papers,  9 conference papers \\
Expected Graduation Date: \textbf{May 2017}\\

\vspace*{-10pt}
\textbf{Mechanical Engineering, Shanghai Jiao Tong University} \hfill\textit{2009-2013}\\
Bachelor of Science, GPA: 91.07/100, Rank: 3/121\\

%----------------------------------------------------------------------------------------
%	SKILL SECTION
%----------------------------------------------------------------------------------------
\vspace*{-10pt}
\section{SKILLS}

\vspace*{-2pt}
\begin{itemize}[leftmargin=*] \itemsep -4pt
	\item {\bf Programming languages:} Matlab, C\#, WPF,  C++, Python, VBA
	\item {\bf Commercial softwares:} Simulink, DeltaV, Microsoft Power BI, AutoCAD, NX Unigraphics
	\item {\bf Research skills:} advanced control, multi-phase flow modeling, time series analysis and prediction, finite difference/volume analysis, convex optimization, stochastic system analysis
\end{itemize}

%----------------------------------------------------------------------------------------
%	INTERN EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{WORK\\ EXPERIENCES}

{\textbf{DeltaV Process Control Intern, Emerson Electric}} \hfill\textit{Summer 2015, Summer 2016}\\
\vspace*{-10pt}
\begin{itemize}[leftmargin=*] \itemsep -3pt
\vspace*{-5pt}
	\item Developed a control performance evaluation tool to automate Loop Service Express (LSE) for chemical plants.
	\item  Automated data collection, analysis and generation of control performance report that identifies top 10 bad PID loops, interacting or fighting  loops, valve issues, excessive operator interference etc.
    \item Got a \$114k  order from a mining company by conducting LSE with the tool and designing a new Model Predictive Control (MPC) strategy .
\end{itemize}

\medskip
{\textbf{Automated Guided Vehicle (AGV) Intern, Singapore Technologies}} \hfill\textit{Summer 2012}\\
\vspace*{-10pt}
\begin{itemize}[leftmargin=*] \itemsep -3pt
\vspace*{-5pt}
	\item Developed and simulated an adaptive Pure Pursuit guidance law for AGV.
\end{itemize}

%----------------------------------------------------------------------------------------
%	SELECTED PROJECTS SECTION
%----------------------------------------------------------------------------------------

\section{SELECTED\\ RESEARCH\\ PROJECTS}
{\textbf{Multi-phase gas kick modeling  (funded company research project)}}\hfill\textit{9/2015-present}\\
\vspace*{-10pt}
\begin{itemize}[leftmargin=*] \itemsep -3pt
\vspace*{-5pt}
	\item Proposed a novel transient multi-phase flow modeling methodology for simulating different well control cases including managed pressure drilling (MPD), underbalanced drilling (UBD) and Wait \& Weight method.
	\item Developed a well control simulator that can run 20-30 times faster than real-time and handle many complexities such as multiple kicks from several formations,  automated choke control,  non-Newtonian drilling fluids, arbitrary wellbore path, area discontinuity, etc.
    \item Helped PI recognize over \$300k in grant funding by completing tasks on time and creating the multi-phase well control simulator. 
\end{itemize}

\medskip
{\textbf{Modeling and control of wind turbine systems (Ph.D. dissertation project)}}\hfill\textit{9/2013-present}\\
\vspace*{-10pt}
\begin{itemize}[leftmargin=*] \itemsep -3pt
\vspace*{-5pt}
    \item Proposed an adaptive gain-scheduled generator torque controller that enhances wind energy harvesting, mitigates fatigue loading on turbine structure, and improves robustness against modeling uncertainties.
	\item Developed an  power scheduling approach that optimizes over probabilistic wind speed prediction obtained from modified Autoregressive and Moving Average (ARMA) analysis.
	\item Proposed a real-time active power controller that enhances power reference tracking and optimizes the performances of hybrid system under instantaneously varying wind speed.
    \item Developed a wind turbine simulation platform  for controller validation and fatigue analysis.
\end{itemize}

\medskip
{\textbf{Electromyography (EMG)-based handwriting recognition}}\hfill\textit{8/2012-5/2013}\\
\vspace*{-10pt}
\begin{itemize}[leftmargin=*] \itemsep -3pt
\vspace*{-5pt}
	\item Applied Dynamic Time Warping (DTW) algorithm to EMG recognition of writing characters.
	\item Improved the average recognition accuracy by 4.65\% after replacing Euclidean Distance with modified Mahalanobis Distance that minimizes the sample interclass variance.
	\item Proposed a real-time two-step signal segmentation method that filters out muscle noise and captures signal of writing characters.
\end{itemize}

\end{resume}
\end{document}
