%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 9pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage[T1]{fontenc}
\usepackage[sc]{mathpazo} % Use the great palatino font provided by the mathpazo package. Add osf for old style figures

\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\usepackage{color}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage[T1]{fontenc}

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\huge\bf Zheren Ma} % Your name at the top
\vspace{-5pt}

\moveleft\hoffset\vbox{\hrule width\resumewidth height .5pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
\moveleft.5\hoffset\centerline{Mechanical Engineering, UT Austin, zhrm@utexas.edu}
\vspace{-10pt}
%\moveleft.5\hoffset\centerline{\color{blue}{\url{http://yuhaozhu.com/}}}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	RESEARCH INTERESTS SECTION
%----------------------------------------------------------------------------------------

\vspace*{-5pt}
%\section{RESEARCH\\ INTERESTS}

%I enjoy research in system modeling, analysis and control.

\section{OBJECTIVE}
Looking for a full-time position in algorithm/software development of control/data analysis

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\vspace*{-10pt}
\section{EDUCATION}

\textbf{The University of Texas at Austin} \hfill\textit{2013-present}\\
Ph.D. Candidate, Mechanical Engineering, GPA: 4.0/4.0\\
Expected Graduation Date: \textbf{May 2017},  Advisor: \href{http://www.me.utexas.edu/~apscl/people.html}{Dongmei Chen}\\

\vspace*{-10pt}
\textbf{Shanghai Jiao Tong University, China} \hfill\textit{2009-2013}\\
B.S., Mechanical Engineering, GPA: 91.07/100\\

%----------------------------------------------------------------------------------------
%	SKILL SECTION
%----------------------------------------------------------------------------------------
\vspace*{-10pt}
\section{SKILLS}

\vspace*{-2pt}
\begin{itemize}[leftmargin=*] \itemsep -4pt
	\item Programming Languages: Matlab/Simulink, C\#, WPF,  C++, Python, VBA
	\item Commercial Softwares: DeltaV, AutoCAD, Unigraphics, Microsoft Power BI
	\item Research skills: advanced control, system modeling, computational fluid dynamics, time series analysis and prediction, finite difference/volume analysis, signal processing
\end{itemize}

%----------------------------------------------------------------------------------------
%	INTERN EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{INTERN\\ EXPERIENCE}

{\textbf{Emerson DeltaV Process Control Intern}} \hfill\textit{Summer 2015, Summer 2016}\\
\vspace*{-10pt}
\begin{itemize}[leftmargin=*] \itemsep -3pt
\vspace*{-5pt}
	\item Developed a C\#/WPF Windows Application for automating control performance evaluation for a chemical plant.
    \item Automated data collection from open platform communication (OPC) server, DeltaV continuous historian, event chronicle, DeltaV configuration etc.
	\item Automated data analysis including  top 10 bad control loops identifications, interacting or fighting  loops detection, valve diagnostics, operator interference analysis etc.
\end{itemize}

\medskip
{\textbf{Singapore Technologies Scholarship Intern}} \hfill\textit{Summer 2012}\\
\vspace*{-10pt}
\begin{itemize}[leftmargin=*] \itemsep -3pt
\vspace*{-5pt}
	\item Implemented an adaptive Pure Pursuit guidance law for automated guided vehicle (AGV).
\end{itemize}

%----------------------------------------------------------------------------------------
%	SELECTED PROJECTS SECTION
%----------------------------------------------------------------------------------------

\section{SELECTED\\ PROJECTS}
{\textbf{Multi-Phase Gas Kick Modeling and Automation}}\hfill\textit{9/2015-present}\\
\vspace*{-10pt}
\begin{itemize}[leftmargin=*] \itemsep -3pt
\vspace*{-5pt}
	\item Proposed a novel multi-phase flow modeling methodology and hydraulic models for simulating different well control cases including managed pressure drilling (MPD), underbalanced drilling (UBD) and Wait \& Weight method.
	\item Developed a Matlab Windows Application for gas kick simulation that can handle many complexities which occur during a well control incident such as handling multiple kicks from one or several formations, dynamic well control, automated choke control, sudden pump start up/shut off, non-Newtonian drilling fluids, arbitrary wellbore path (including directional and horizontal wells), area discontinuity, etc.
\end{itemize}

\medskip
{\textbf{Modeling and Simulation of Vibrations in a Drilling System}}\hfill\textit{2/2015-5/2015}\\
\vspace*{-10pt}
\begin{itemize}[leftmargin=*] \itemsep -3pt
\vspace*{-5pt}
	\item Modeled drill string vibration by using the wave propagation theory and a comprehensive rock-bit interaction model.
	\item Conducted vibration analysis including bit-bounce, stick-slip and bit whirl.
\end{itemize}

\medskip
{\textbf{Control of a Integrated Wind Turbine and Battery System}}\hfill\textit{6/2014-11/2014}\\
\vspace*{-10pt}
\begin{itemize}[leftmargin=*] \itemsep -3pt
\vspace*{-5pt}
	\item Developed an efficient and reliable power scheduling approach that applied model predictive control (MPC) to probabilistic wind speed forecast.
	\item Proposed a real-time active power controller that enhances power reference tracking and optimizes the performances of hybrid system under instantaneously varying wind speed.
\end{itemize}

\medskip
{\textbf{Wind Turbine Control During Partial Load Operation}}\hfill\textit{9/2013-5/2014}\\
\vspace*{-10pt}
\begin{itemize}[leftmargin=*] \itemsep -3pt
\vspace*{-5pt}
	\item Proposed an adaptive generator torque controller that  improved turbine performances in terms of wind energy harvesting, fatigue loading mitigation, and better robustness against model uncertainties.
    \item Developed a Matlab/Simulink Windows Application for wind turbine controller validation and fatigue analysis.
\end{itemize}


%----------------------------------------------------------------------------------------
%	TEACHING EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\section{TEACHING/\\RESEARCH EXPERIENCE}
\begin{itemize}[leftmargin=*] \itemsep -2pt
\vspace*{-2pt}
	\item Graduate Research Assistant in Petroleum Engineering \hfill\textit{9/2015-present}
	\item Graduate Research Assistant in Mechanical Engineering \hfill\textit{1/2015-5/2015}
	\item Teaching Assistant of Engineering Computational Methods \hfill\textit{9/2013-12/2014}
\end{itemize}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

%\vspace*{-5pt}
\section{PUBLICATIONS}

{\large\textbf{Journal Papers}}
\begin{itemize}[leftmargin=*] \itemsep 0pt
%\vspace*{-5pt}
	\item \underline{Zheren Ma}, Zeyu Yan, Mohamed L. Shaltout, Dongmei Chen, 
          \href{http://ieeexplore.ieee.org/xpl/login.jsp?tp=&arnumber=7065260&url=http\%3A\%2F\%2Fieeexplore.ieee.org\%2Fxpls\%2Fabs_all.jsp\%3Farnumber\%3D7065260}
          {``Optimal real-time control of wind turbine during partial load operation''}
          \textit{IEEE Transactions on Control Systems Technology}, vol. 23, no. 6, pp. 2216-2226, 2015.

\item \underline{Zheren Ma}, Mohamed L. Shaltout, Dongmei Chen, 
          \href{http://dynamicsystems.asmedigitalcollection.asme.org/article.aspx?articleid=2468735}
          {``An Adaptive Wind Turbine Controller Considering Both the System Performance and Fatigue Loading''}, 
          \textit{Journal of Dynamic Systems, Measurement, and Control}, vol. 137, no. 11, p. 111007, 2015.

\item Liang Gong, Yan Xi, \underline{Zheren Ma}, Chengliang Liu, 
          \href{http://link.springer.com/article/10.1007\%2Fs12204-013-1371-8}
          {``Modeling, identification and simulation of DC resistance spot welding process for aluminum alloy 5182''}, 
          \textit{Journal of Shanghai Jiaotong University}, vol. 18, no. 1, pp. 101-104, 2013.
\end{itemize}

{\large\textbf{Conference Papers}}
\begin{itemize}[leftmargin=*] \itemsep 0pt
%\vspace*{-5pt}
    \item \underline{Zheren Ma}, Brandon Li, Zeyu Yan,
         \href{http://ieeexplore.ieee.org/xpl/login.jsp?tp=&arnumber=7444317&url=http\%3A\%2F\%2Fieeexplore.ieee.org\%2Fxpls\%2Fabs_all.jsp\%3Farnumber\%3D7444317}
          {``Wearable driver drowsiness detection using electrooculography signal''}, 
          \textit{IEEE Topical Conference on Wireless Sensors and Sensor Networks}, pp. 41-43, 2016.

	\item \underline{Zheren Ma}, Dongmei Chen, 
          \href{http://proceedings.asmedigitalcollection.asme.org/proceeding.aspx?articleid=2481922}{``Modeling of coupled axial and torsional motion of a drilling system''}, 
          \textit{ASME Dynamic Systems and Control Conference}, pp. V002T20A005, 2015.

	\item \underline{Zheren Ma},  Dongmei Chen, 
          \href{http://ieeexplore.ieee.org/xpl/login.jsp?tp=&arnumber=7171801&url=http\%3A\%2F\%2Fieeexplore.ieee.org\%2Fxpls\%2Fabs_all.jsp\%3Farnumber\%3D7171801}
          {``Optimal power dispatch and control of a wind turbine and battery hybrid system''}, 
          \textit{American Control Conference}, pp. 3052-3057, 2015.

	\item \underline{Zheren Ma}, Mohamed L. Shaltout, Dongmei Chen, 
          \href{http://proceedings.asmedigitalcollection.asme.org/proceeding.aspx?articleid=2086149}
          {``Adaptive gain modified optimal torque controller for wind turbine partial load operation''}, 
          \textit{ASME Dynamic Systems and Control Conference}, pp. V002T18A002, 2014.

	\item \underline{Zheren Ma}, Liang Gong, Yanming Li, Chengliang Liu, 
          \href{http://ieeexplore.ieee.org/xpl/login.jsp?tp=&arnumber=6618166&url=http\%3A\%2F\%2Fieeexplore.ieee.org\%2Fxpls\%2Fabs_all.jsp\%3Farnumber\%3D6618166}
          {``CMAC-based real-time calculation of the effective welding current during AC resistance spot welding''}, 
          \textit{IEEE International Conference on Mechatronics and Automation}, pp. 1669-1674, 2013.

    \item Mohamed L. Shaltout, \underline{Zheren Ma}, Dongmei Chen, 
         \href{http://ieeexplore.ieee.org/xpl/login.jsp?tp=&arnumber=7525406&url=http\%3A\%2F\%2Fieeexplore.ieee.org\%2Fxpls\%2Fabs_all.jsp\%3Farnumber\%3D7525406}
          {``An economic model predictive control approach using convex optimization for wind turbines''}, 
          \textit{American Control Conference}, pp. 3176-3181, 2016.
          
    \item Chengzhang Li, \underline{Zheren Ma}, Lin Yao, Dingguo Zhang, 
          \href{http://ieeexplore.ieee.org/xpl/login.jsp?tp=&arnumber=6609958&url=http\%3A\%2F\%2Fieeexplore.ieee.org\%2Fiel7\%2F6596169\%2F6609410\%2F06609958.pdf\%3Farnumber\%3D6609958}
          {``Improvements on EMG-based handwriting recognition with DTW algorithm''}, 
          \textit{ International Conference of Engineering in Medicine and Biology Society}, pp. 2144-2147, 2013.
          
    \item \underline{Zheren Ma}, Ali Karimi Vajargah, Pradeep Ashok, Dongmei Chen, Eric van Oort, Roland May, David Curry, John MacPherson, Gerald Becker, 
        {``Multi-Phase well control analysis during managed pressure drilling operations''}, 
       \textit{SPE Annual Technical Conference and Exhibition}, 2016.

    \item \underline{Zheren Ma}, Brandon Li, Zeyu Yan, Dongmei Chen, Wei Li, 
        {``Wearable sleepiness detection based on characterization of physiological dynamics''}, 
       \textit{ASME Dynamic Systems and Control Conference}, 2016.
\end{itemize}

%----------------------------------------------------------------------------------------
%	COURSEWORK SECTION
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%	HONOR SECTION
%----------------------------------------------------------------------------------------

\section{GRADUATE COURSEWORK}

\vspace*{-1pt}
\begin{itemize}[leftmargin=*] \itemsep -2pt
	\item Advanced vehicle powertrain system, Modeling and simulation of multi-energy system, Computational fluid mechanics, Digital signal processing, Modern control, Time-series modeling/analysis/Control, Optimal control theory, Multi-variable control system, Digital control, Stochastic systems and control
\end{itemize}

%----------------------------------------------------------------------------------------

\end{resume}
\end{document}
